%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[12pt, letter, oneside]{Thesis} % Paper size, default font size and one-sided paper
%\graphicspath{{Pictures/}} % Specifies the directory where pictures are stored
\usepackage{hyperref} % For internal referencing
\usepackage{lipsum} % For generating fill text for trouble-shooting LaTex
\usepackage{setspace} % For picking line spacing *within* sections
\usepackage{parskip} % For changing spacing between heads, lets me use linebreaks for spacing between paragraphs
\usepackage{float}% For Figures
	\floatstyle{plain}
	\restylefloat{figure}
	\usepackage{rotating} % For rotating figures ±90˚ use \begin{sidewaysfigure}	
%% Pick my Font
	% For Palatino
	%\usepackage[sc]{mathpazo}
	%	\linespread{1.05} % Palatino needs more leading (space between lines)
	% For Ariel
	\usepackage{helvet}
	\renewcommand{\familydefault}{\sfdefault}

% Center the Chapter and heading titles 
% http://tex.stackexchange.com/questions/23858/center-chapter-book-class
	\usepackage{titlesec}
	\titleformat{\chapter}[display]
	{\normalfont\huge\bfseries\centering}{\chaptertitlename\ \thechapter}{20pt}{\Huge}

\usepackage[T1]{fontenc} 
\usepackage{flexisym} % Lets me use prime symbols
\usepackage{gensymb} % For degree '\degree'

% For Referencing
\usepackage[square, comma, sort&compress]{natbib} 
	\setlength{\bibsep}{0.0pt} % Reduce size of bibliography
	% Use the natbib reference package - read up on this to edit the reference style; if you want text (e.g. Smith et al., 2012) for the in-text references (instead of numbers), remove 'numbers' 
% Colors hyperlinks in blue - change to black if annoying	
\hypersetup{urlcolor=blue, colorlinks=true}  

%% To highlight things for later review
\usepackage{soul} % use \hl{this is some highlighted text}

%% For Inserting Code | http://stackoverflow.com/questions/3175105/how-to-insert-code-into-a-latex-doc
\usepackage{listings}
\usepackage{color}
	\definecolor{dkgreen}{rgb}{0,0.6,0}
	\definecolor{gray}{rgb}{0.5,0.5,0.5}
	\definecolor{mauve}{rgb}{0.58,0,0.82}

	\lstset{frame=tb,
	  language=Perl,
	  aboveskip=3mm,
	  belowskip=3mm,
	  showstringspaces=false,
	  columns=flexible,
	  basicstyle={\small\ttfamily},
	  numbers=none,
	  numberstyle=\tiny\color{gray},
	  keywordstyle=\color{blue},
	  commentstyle=\color{dkgreen},
	  stringstyle=\color{mauve},
	  breaklines=true,
	  breakatwhitespace=true
	  tabsize=3
	}

\title{\ttitle} % Defines the thesis title - don't touch this
%----------------------------------------------------------------------------------------
% Organism names
%----------------------------------------------------------------------------------------
\newcommand\flies{\textit{Drosophila melanogaster}} %Done
\newcommand\locusts{\textit{Schistocerca gregaria}} % Done
\newcommand\worms{\textit{Caenorhabditis elegans}} % Done


%----------------------------------------------------------------------------------------
\begin{document}
%----------------------------------------------------------------------------------------

\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages
\setstretch{1.3} % Line spacing of 1.3

% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{} % Clears all page headers and footers
\rhead{\thepage} % Sets the right side header to show the page number
\lhead{} % Clears the left side page header
\pagestyle{fancy} % Finally, use the "fancy" page style to implement the FancyHdr headers
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % New command to make the lines in the title page

% PDF meta-data
\hypersetup{pdftitle={\ttitle}}
\hypersetup{pdfsubject=\subjectname}
\hypersetup{pdfauthor=\authornames}
\hypersetup{pdfkeywords=\keywordnames}

%----------------------------------------------------------------------------------------
%	TITLE PAGE Umass
%----------------------------------------------------------------------------------------
\begin{titlepage}
\begin{center}
	\huge EXAMINATION OF DYNAMIC LONG RNAS\\[2cm] 
	{\large 
		A Dissertation Presented \\[1cm]
		By \\[1cm]
		Christian K. Roy \\[1cm]
		Submitted to the Faculty of the University of the \\
		Massachusetts Graduate School of Biomedical Sciences, Worcester\\
		in partial filfillment of the requirements\\
		for the degree of \\[2cm]
		DOCTOR OF PHILOSOPHY \\[1cm]
		MAY 21st 2014\\[1cm]
		BIOCHEMISTRY\\[1cm]
 	}
 \end{center}
 \end{titlepage}
%----------------------------------------------------------------------------------------
%	Signature Page Umass
%----------------------------------------------------------------------------------------
\begin{titlepage}\label{hd:titlePage}
\begin{center}
		EXAMINATION OF DYNAMIC LONG RNAS\\[0.25cm]

		A Dissertation Presented \\[0.25cm]
		By \\[0.25cm]
		Christian K. Roy \\[0.25cm]
 
		The signatures of the Dissertation Defense Committee signify \\
		completion and approval as to style and content of the Dissertation\\[1cm]
		\rule[1em]{25em}{1pt}\\[-0.6cm]% This prints a line for the signature
		Melissa J. Moore, Co-Thesis Advisor\\[1cm]
		\rule[1em]{25em}{1pt}\\[-0.6cm]
		Phillip D. Zamore, Co-Thesis Advisor\\[1cm]
		\rule[1em]{25em}{1pt}\\[-0.6cm]
		Scot Wolfe, Member of Committee\\[1cm]
		\rule[1em]{25em}{1pt}\\[-0.6cm]
		Job Dekker, Member of Committee\\[0.25cm]
		The signature of the Chair of the Committee signifies that the written
		dissertation meets the requirements of the Dissertation Committee\\[1cm]
		\rule[1em]{25em}{1pt}\\[-0.6cm]
		Zhiping Weng, Chair of Committee\\[0.25cm]
		The signature of the Dean of the Graduate School of Biomedical Sciences signifies that the student has met all graduation requirements of the school.\\[1cm]
		\rule[1em]{25em}{1pt}\\[-0.6cm]
		Anthony Carruthers, Ph.D.,\\[0.25cm]
		Dean of the Graduate School of Biomedical Sciences\\[0.25cm]
		Biochemistry and Molecular Pharmacology\\[0.25cm]
		MAY 21st 2014 

 \end{center}
 \end{titlepage}
\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------

\addtotoc{Abstract} % Add the "Abstract" page entry to the Contents
\label{hd:abstract}
\abstract{\addtocontents{toc}{\vspace{1em}} % Add a gap in the Contents, for aesthetics

The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots

}
\setcounter{page}{3}
\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\setstretch{1.3} % Reset the line-spacing to 1.3 for body text (if it has changed)

\acknowledgements{\addtocontents{toc}{\vspace{1em}} % Add a gap in the Contents, for aesthetics
\label{hd:acknowledgements}
First I would like to acknowledge and thank Laura Geagan and Rebecca Sendak at Genzyme. They were my supervisors while I was a research associate there, and assisted and encouraged my transition back to graduate school. Without the confidence they instilled in my abilities as a young scientist in, I doubt I would have ever signed up for more school. 

Next I’d like to thank Melissa. During my 1st year retreat at Wood’s Hole I first learned that Melissa is a fantastic communicator of interesting and important science. When she brought out her rope representing the unspliced pre-mRNA of dystrophin—a rope that reached to the back of a rather large auditorium—and then dramatically held up a No.2 pencil representing the final mRNA product, both to scale, I knew the that I wanted to do my graduate research in her lab. I have never once doubted the decision to join Melissa’s lab, and have learned so much from the broad and interconnected approach she takes to important scientific questions. Thank you so much for teaching me to always consider the big picture, go for the answer, and to just ask when I need help.

Soon after joining Melissa’s lab, and a project going well, it was proposed to me that I be a joint student between Melissa and Phil. It was not difficult to not jump at the opportunity to be advised by two Howard Hughes Investigators, and I also haven’t regretted the decision. Over the past few years, I have been continually amazed at the depth of Phil’s knowledge, in scientific and general topics. He is a careful, meticulous, quantitative, and calculating mentor. While I feel that I clicked ‘on the level’ with Melissa, interacting with Phil forced me to think and act outside my comfort zone, something I always tell myself is a critical aspect of change and growth. Thank you Phil for everything I’ve learned.

My committee has also been very supportive throughput my PhD. I hardly believed the ease with which I passed my qualifying exam, and took it as a big confidence boost. The following years of TRAC meetings confirmed that I was not thinking way off-base. The one-on-one meetings just prior to my QE were especially helpful. Thanks to Scot, Job, and especially Zhiping for all the guidance.

\begin{itemize}

  \item Lab Members;  Aaron; Alper; Amrit
  \item Eric and Erin
  \item Collaborators
  \item Dave Weaver
  \item Muro
  \item Graveley
  \item Heinrich
  \item Anna
  \item Ogo
  \item Family
  \item Jul Owen

\end{itemize}

}

\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------
% The page style headers have been "empty" all this time, 
% now use the "fancy" headers as defined before to bring them back
\pagestyle{fancy} 
\lhead{\emph{Contents}} % Set the left side page header to "Contents"
	\tableofcontents % Write out the Table of Contents
\lhead{\emph{List of Figures}} % Set the left side page header to "List of Figures"
	\listoffigures % Write out the List of Figures
\lhead{\emph{List of Tables}} % Set the left side page header to "List of Tables"
	\listoftables % Write out the List of Tables
%----------------------------------------------------------------------------------------
%	ABBREVIATIONS
%----------------------------------------------------------------------------------------
\clearpage % Start a new page
\setstretch{1.5} % Set the line spacing to 1.5, this makes the following tables easier to read
\lhead{\emph{List of Abreviations}}
\label{hd:abrevs} \listAbreviations
\begin{table}[h]
\begin{tabular}{l|l}
AS       & Alternative Splicing                                 \\
DNA      & Deoxyribonucleic acid                                \\
ssDNA    & Single-stranded DNA                                  \\
RNA      & Ribonucleic acid                                     \\
ssRNA    & Single-stranded RNA                                  \\
ATP      & Adenosine triphosphate                               \\
NAD      & Nicotinamide adenine dinucleotide                    \\
ChIP-Seq & Chromatin Immunoprecipitation followed by sequencing \\
HTS      & High-throughput sequencing (see also NGS)            \\
NGS      & Next-generation sequencing                           \\
nt       & A nucleotide of either DNA or RNA                    \\
bp       & A base pair of DNA                                   \\
SRE      & Splicing Regulatory Element                          \\
IRE      & Intron Recognition Element                           \\
CNS      & Central Nervous System                               \\
TSS      & \{Transcription or Translation\} Start Site          \\
TTS      & \{Transcription or Translation\} Termination Site    \\
SAGE     & Serial Analysis of Gene Expression                   \\
\end{tabular}
\end{table}

%----------------------------------------------------------------------------------------
%	SYMBOLS
%----------------------------------------------------------------------------------------
\clearpage % Start a new page
\lhead{\emph{List of Symbols}}
\label{hd:Symbols} \listSymbols

\begin{table}[h]
\begin{tabular}{ll}
5\textprime       & The 5 prime end of a DNA or RNA molecule 			\\
3\textprime       & The 5 prime end of a DNA or RNA molecule 			\\
$\mu$       	  & Micro. A value of 1x10\textsuperscript{-6} standard units 			\\
\end{tabular}
\end{table}

%----------------------------------------------------------------------------------------
%	Definitions
%----------------------------------------------------------------------------------------
\clearpage % Start a new page
\lhead{\emph{Definitions}}
\label{hd:Definitions} \listDefinitions

\begin{description}
  \item[RNA-Seq] \hfill \\
  A technology wherein RNA is fragmented, converted to DNA, and analyzed on a high-throughput sequencing instrument
  \item[A ‘Read’] \hfill \\
  The sequence of nucleotides produced from each spot on a high-throughput sequencing machine
  \item[Insert] \hfill \\
  The RNA molecule captured between two cloning sequences in a high-throughput sequencing library preparation workflow
    \item[Read length] \hfill \\
  The number of nucleotides for each given 'read'
    \item[Read depth] \hfill \\
  The number of reads obtained from each high-throughput sequencing analysis
    \item[Coverage] \hfill \\
  A measure of the number of times each nt of a genome is sequenced. E.g. 100 million reads of a 10 million nt genome = 10X coverage, assuming uniform distribution of the 'reads'
    \item[Paired-end] \hfill \\oach1995a
  When both sides of a DNA insert or template are sequenced, utilizing the original length of DNA between the reads to facilitate mapping (\cite{Roach1995}).
    \item[Scaffold or contig] \hfill \\
  A draft sequence of nucleotides, meant to represent the actual biological sequence as closely as possible, examples include unassembled fragments of chromosomes or fragments of mRNA transcripts.
    \item[Argonaute] \hfill \\
  Protein(s) belonging to a group containing a Piwi (P-element induced wimpy testes) domain, that bind nucleic acids and participate in many target-guided processes, including RNA Interference, and RNA-indicuded transcript/gene silencing.   
\end{description}
\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------
\setstretch{1.3} % Return the line spacing back to 1.3
\pagestyle{empty} % Page style needs to be empty for this page
\label{hd:Dedicatory}
\dedicatory{
	I would like to dedicate this Doctoral dissertation to my grandfather, George Knauf. My grandfather passed away on September 23rd, 2011, just one week shy of his 82nd birthday. I find it difficult to articulate how much I miss him. He spoke carefully and never without purpose or conviction. While I hear from others that he was proud of me, he rarely, if ever, betrayed that type of emotion directly. It is my goal to build as solid a life as he, founded on hard work, playing the long game, responsibility, and maintaining friendships. These are just a few of the personality traits that I observed and try to emulate. The fact that he passed before he could meet our son Owen is one of my biggest regrets. Of all the possessions he left behind, it is the memory of our time together that I will cherish the most. Rest in peace, Grump. I did it. 
} % Dedication text
\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics
\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	Preface
%----------------------------------------------------------------------------------------

\prefaceSection

The work reported in this dissertation has been published in the following articles.
Chapter \ref{Chapter4} has been published previously as:\\
Li, X. Z. Z., Roy, C. K. K., Dong, X., Bolcun-Filas, E., Wang, J., Han, B. W. W., … Zamore, P. D. D. (2013). An Ancient Transcription Factor Initiates the Burst of piRNA Production during Early Meiosis in Mouse Testes. Molecular Cell, 50(1), 1–15. doi:10.1016/j.molcel.2013.02.016

Some contents of Chapter \ref{Chapter3} are included in a currently submitted manuscript. 

\clearpage

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - CHAPTERS
%----------------------------------------------------------------------------------------

\mainmatter % Begin numeric (1,2,3...) page numbering
\pagestyle{fancy} % Return the page headers back to the "fancy" style
%\setstretch{2} % Line spacing of 2
\setstretch{1} % Line spacing of 1
\label{hd:Chatpers}
\input{Chapters/Chapter1-Introduction}
\input{Chapters/Chapter2-SeqZipMethodology} 
\input{Chapters/Chapter3-SeqZipManuscript}
\input{Chapters/Chapter4-MolCel2013} 
\input{Chapters/Chapter5-Discussion} 


%----------------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDICES
%----------------------------------------------------------------------------------------

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

\appendix % Cue to tell LaTeX that the following 'chapters' are Appendices
\label{hd:Appendicies}
% Include the appendices of the thesis as separate files from the Appendices folder
% Uncomment the lines as you write the Appendices

\input{Appendices/AppendixA}
%\input{Appendices/AppendixB}
%\input{Appendices/AppendixC}

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

%----------------------------------------------------------------------------------------
\backmatter
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------
\label{hd:Bibliography}
\setstretch{1} % Line spacing of 1
% Change the page header to say "Bibliography"
\lhead{\emph{Bibliography}} 
% Use the "unsrtnat" BibTeX style for formatting the Bibliography
%\bibliographystyle{unsrtnat}
\bibliographystyle{plainnat}
% The references are stored in the file named "library.bib.bib"
\bibliography{library.bib} 

\end{document}  