% !TEX root = /Users/royc/Google_Drive/Thesis/RoyC_Umass_Thesis.tex
\setstretch{1} 
\acknowledgements{}\label{hd:acknowledgements}

First I would like to acknowledge and thank Laura Geagan and Rebecca Sendak at Genzyme. They were my supervisors while I was a research associate there, and assisted and encouraged my transition back to graduate school. Without the confidence they instilled in my abilities as a young scientist, I doubt I would have ever signed up for more school. 

Next I’d like to thank Melissa. During my 1st year retreat at Wood’s Hole I first observed Melissa's ability as a fantastic communicator of interesting and important science. When she brought out her rope representing unspliced pre-mRNA of dystrophin\textendash a rope that reached to the back of a rather large auditorium\textendash and then dramatically held up a ``No.2'' pencil representing the final mRNA product, both to scale, I knew the that I wanted join her lab. 

Soon after joining Melissa’s lab, with a project going well, it was proposed to me that I be a joint student between Melissa and Phil. It was not difficult to not jump at the opportunity to be advised by \textit{two} Hughes Investigators. I haven’t regretted the decision. Over the past few years, I have been continually amazed at the depth of Phil’s knowledge, in scientific and general topics. He is a careful, meticulous, quantitative, and calculating mentor. Interactions with Phil force me to think and act outside my comfort zone, something I always tell myself is a critical aspect of change and growth. Thank you Phil for everything I’ve learned.

My committee has also been very supportive throughput my PhD. I hardly believed the ease with which I passed my qualifying exam, and took it as a big confidence boost. The following years of TRAC meetings confirmed that I was not thinking way off-base. The one-on-one meetings just prior to my QE were especially helpful. Thanks to Scot, Job, and Zhiping for all the guidance.

I would like to thank all members of the Za(Moore) labs, past and present. Specifically I would like to thank other members of my year in the Moore Lab, Eric and Erin. Also thanks to fantastic past post-docs Amrit and Aaron\textendash thanks for all the help! Thank you to Alper, Bo, and Can for my novice bioinformatic questions.

Thanks to other faculty I have interacted with throughout my time at Umass, including Dave Weaver, Brent Graveley, Andres Muro, Manuel Garber, and Heinrich Gottlinger. And thanks to Anna from the Gottlinger lab for involving me in her HIV and hUPF1 story.

My project was pushed forward by a pair of great rotation students: Ben Landry and Ogooluwa Adegoke Ojelabi (Ogo). Thanks you two for letting me know the SeqZip method was robust beyond my own hands.

My family, while small, always instilled the importance and value of education. Thank you Mom, Dad, Grandpa and Grandma for providing me with so much opportunity. I hope I have made you proud.

Finally, and most importantly, I would like to acknowledge the love and support of my wife, Julie. Much of my success can be attributed to her hard work and support over the last 15 years. Our son, Owen, is lucky to have such an amazing mom. Our family is truly blessed.  Thanks P :)

\clearpage % Start a new page